Weakly Nonlinear MRI: Notes

### 2014-06-10 notes/mri_notes.tex
another figure

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{s_Re_Im_Co_coarse}
\caption{Real and Imaginary parts of parameter space for linear MRI system.}
\label{onoff}
\end{figure*}

By solving the linear MRI system on a coarse parameter space grid. \\

>>>>

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{s_Re_Im_Co_coarse}
\caption{Real and Imaginary parts of parameter space for linear MRI system: coarse grid}
\end{figure*}

By solving the linear MRI system on a coarse parameter space grid. We then zoom in to find the critical values of $\reym$ and $Q$:\\

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{s_Re_Im_Co_finegrid3}
\caption{Real and Imaginary parts of parameter space for linear MRI system: fine grid}
\end{figure*}

The code that produces the above is in \texttt{multirun\_paramspace.py}, which runs\\ \texttt{multirun\_linear\_MRI.py}. \\

From this investigation, I have been using $Q = 0.75$, $\reym = 4.877$, rather than the $\reym \sim 4.9$ given in Umurhan+. The adjoint homogenous solution, however, still does not resemble the one found in Umurhan+. Our solution is shown in Figure \ref{AHsol}:

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{adjoint_soln_incorrect}
\caption{Adjoint homogenous solution.}
\label{AHsol}
\end{figure*}

While this solution is symmetric about the origin, as expected, it does not have the same shape as the solution in Umurhan+.
